A Unification of Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-23 colt-21/cvx-flats.tex
Looking at Raf's feedback and adjusting and fixing Corollary 28.  it's really verbose now, but type checks

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\prop}[2][\mathcal{P}]{\mathrm{prop}_{#1}[#2]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{cc\,dim}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\spn}{\mathrm{span}}

@@

\begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
	\begin{equation}
	  d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
	\end{equation}
%% Bo: old version, Jun 4 7pm
%%	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
%%	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
%%	\begin{equation}
%%	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
%%	\end{equation}\jessiet{TODO: add minnability\bo{Tried!}}
\end{restatable}
\begin{proof}[Proof sketch]
	%\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
	\jessie{Redid this citing Lemma~\ref{lem:finite-relint-dim} instead}
	First, take $p \in \relint{\simplex}$ for intuition, so $\|p\|_0 = n$.
	Lemma~\ref{thm:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \spn(F - \{p\}) \geq n - d- 1$ is given by chaining ~\ref{lem:finite-relint-dim} (ii) and Lemma~\ref{lem:Fp-subset-feasible-subset}.
%	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
%	%dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$. 
%	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
%	Moreover, this implies $\dim(\Sc_{\gamma_r}(p)) \geq \codim(W) = n - d - 1$, completing the proof for $p \in \relint{\simplex}$.

@@

\begin{lemma}\label{lem:finite-relint-dim}
  Let the $d$-flat $F\subseteq \P$ (defined over finite $\Y$) contain some $p\in\relint{\P}$.
  Then 
  \begin{enumerate}
  	\item[(i)] $p \in \relint{F}$; 
  	\item[(ii)] $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  \raf{Moved; see margin comment:  for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
    (Such a function must exist by $F$ being a $d$-flat.)}

  (i)
  Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P$\raft{You want the quantification order of $\epsilon$ and $q$ swapped I think; also, add ``for all'' for clarity}, $\alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
  In particular, for $q \in F$, we claim $q_\alpha \in F$.
  \raft{$V$ comes out of nowhere here, and then in the next bullet you introduce $W$ for the same thing. Better to do all that before both bullets. ``As $F$ is a $d$-flat, we have some $W$... $F=\zeros{W}$''.  Also, okay to just write $\E_p W$ not $\E_p W(Y)$, since technically $W$ is a random variable.}
  As $p,q \in F$, we have $\E_pV = \E_qV = \vec 0$.
  By linearity of expectation, we then have $\E_{q_\alpha} V = \vec 0$.
  % (Y) = \E_p V(Y) - \alpha(\E_q V(Y) - \E_p V(Y)) = \vec 0 - \alpha(\vec 0 - \vec 0) = \vec 0$.
  This implies $q_\alpha \in F$, and therefore $p \in \relint{F}$.

  (ii)
  Define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W:\spn(\P_p)\to\reals^d, v\mapsto \E_v W$.
  We first show $\spn(F_p) = \ker(T_W)$.
  Let $v \in \ker(T_W)$. % = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
  From (i), as $p \in \relint{\P}$, we have $\vec 0 \in \relint{F_p}$.
  Thus there is some $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$.
  Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
  Hence, $\spn(F_p) = \ker(T_W)$.\jessie{Right?}\raf{Why? Hint: you want to show $v$ is in the span of $F_p$; in fact, it's a scalar multiple of something in $F_p$.}

  As $\Y$ is a finite set, $\spn(\P_p)$ is a finite-dimensional vector space.
  The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p))$.
  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\spn(F_p) = \ker(T_W)$, the conclusion follows.\raft{Worth checking the diff for what I changed. Inequality was backwards :-)}
  % 
  %	Now let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
  %	There must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$ $p \in \relint{\P}$ implies $\vec 0 \in \relint{F_p}$ by (1.).
  %	Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
  %	This allows us to conclude $\spn(F_p) = \ker(T_W)$.\jessie{Right?}
  %	
  %	We want to show $F_p = \P_p \cap \ker(T_W)$, then derive the result from there. \jessie{I don't see why this is necessary.}
  %	
  %	In order to see this, consider $v \in F_p \iff v + p \in F$, and similarly for $\P_p$.
  %	Now, as $F \subseteq \P$ by construction, we have $F_p \subseteq \P_p$, and since $\spn(F_p) = \ker(T_W)$, we additionally have $F_p \subseteq \ker(T_W)$, yielding $F_p \subseteq \P_p \cap \ker(T_W)$.
  %	Now consider $v \in \P_p \cap \ker(T_W)$; we know that $\E_v W = \vec 0$, and therefore, $\E_{q} W = \vec 0$, so $v \in F_p$, thus $F_p = \P_p \cap \ker(T_W)$.
  %	
  %	Since $\spn(F_p) = \ker(T_W)$, we have $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(\P_p)) - d$ by \jessie{isomorphism theorem} since $F_p = \ker(T_W) \cap \P_p$. \jessie{??}
\end{proof}

\begin{lemma}\label{lem:Fp-subset-feasible-subset}
Suppose we are given $p \in \relint{\P}$, property $\gamma: \P \toto \R$, and report $r \in \gamma(p)$.
If $\gamma$ is indirectly elicited by a convex $L \in \L_d$, then there is a $d$-flat $F$ such that $p \in F$ and $F_p := F - \{p\} \subseteq \Sc_{\gamma_r}(p)$.	
\end{lemma}
\begin{proof}
	Construct $F$ as in Theorem~\ref{thm:convex-flats-inf-dim}\raft{Lemma?}; $F$ is a $d$-flat, contains $p$, and we have $F \subseteq \gamma_r$.
	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
	By Lemma~\ref{lem:finite-relint-dim}(i), we know $p \in \relint{F}$, and therefore, $\vec 0 \in \relint{F_p}$.
	Consider $v \in F_p$.
	By $F_p$ being convex and $\vec 0 \in \relint{F_p}$, we know there exists an $\alpha > 0$ so that $-\alpha v \in F_p$.
	This implies $p - \alpha v \in F \implies p - \alpha v \in \gamma_r \implies v \in \Sc_{\gamma_r}(p)$ since $F$ and $\Sc_{\gamma_r}(p)$ are convex and $F \subseteq \gamma_r$.
	This yields the desired result, $F_p \subseteq \Sc_{\gamma_r}(p)$.\raft{It feels weird how redundant this is from the argument in the 1st paragraph of (ii) above, but okay for now.}
\end{proof}

@@

Now, suppose for contradiction that $q \not\in \gamma_{r'}$.\jessiet{I think this count be made more concise, but is clearest this way; it's a bit tricky with the movement between discussing flats and hyperplanes and being subsets of level sets, etc.}
Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
This contradicts the assumption $F \subseteq \gamma_r$.
Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
Because $r$ and $r'$ were completely symmetric, this completes the proof.

% %commented out 01.22.2021 - Jessie; incorporating Lemma that says p in relint(F)	
%	Suppose $F \subseteq \gamma_r$.
%	We show $F \subseteq \gamma_{r'}$.
%	Let $q \in F$.
%	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F$ as well.
%	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\P$ follows because $p \in \relint\P$. \jessie{Does $\relint{F}$ actually come in here?}
%	
%	Now, suppose for contradiction that $q \not\in \gamma_{r'}$.
%	Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
%	But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
%	This contradicts the assumption $F \subseteq \gamma_r$.
%	Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
%	Because $r$ and $r'$ were completely symmetric, this completes the proof.
\end{proof}

@@

\hariresult*
\begin{proof}
	Let $L : \reals^d \times \Y \to \reals$ be a calibrated surrogate for $\ell$, and consider $\Y' := \supp(p)$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y'$.
	Take $L' := L|_{\Y'}$ and $\ell' := \ell|_{\Y'}$.

	First, observe $L'$ (eliciting $\Gamma$) indirectly elicits $\gamma' := \prop{\ell'}$ since, for all $p \in \simplex$, and therefore all $p \in \Delta_{\Y'}$, we have $p \in \Gamma_u \implies p \in \gamma_{\psi(u)}$, and $\Gamma(p) = \Gamma'(p)$ and $\gamma(p) = \gamma'(p)$ for $p \in \Delta_{\Y'}$.
	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $p \in \simplex$, and therefore for all $p \in \simplexp$ by equality of $\gamma$ and $\gamma'$ for $p \in \simplexp$.

>>>>

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\simplex}{\Delta_\Y}
\newcommand{\relint}[1]{\mathrm{relint}(#1)}
\newcommand{\prop}[2][\mathcal{P}]{\mathrm{prop}_{#1}[#2]}
\newcommand{\elic}{\mathrm{elic}}
\newcommand{\eliccvx}{\mathrm{elic}_\mathrm{cvx}}
\newcommand{\elicpoly}{\mathrm{elic}_\mathrm{pcvx}}
\newcommand{\elicembed}{\mathrm{elic}_\mathrm{embed}}
\newcommand{\ccdim}{\mathrm{cc\,dim}}
\newcommand{\rank}{\mathrm{rank}}
\newcommand{\proj}{\mathrm{proj}}
\newcommand{\supp}{\mathrm{supp}}
\newcommand{\spn}{\mathrm{span}}

@@

\begin{restatable}[\cite{ramaswamy2016convex} Theorem 18]{corollary}{hariresult}\label{cor:fsd-bound}
	Let $\ell:\R \times \Y \to \reals$ be a discrete loss eliciting $\gamma:\simplex \toto \R$, and let $L \in \L_d$ be a minimizable consistent convex surrogate for $\ell$.
	Then for all $p \in \simplex$ and $r \in \gamma(p)$,
	\begin{equation}
	  d \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
	\end{equation}
%% Bo: old version, Jun 4 7pm
%%	Suppose we are given a discrete loss $\ell:\R \to \reals^\Y_+$ eliciting $\gamma$.
%%	Take $p \in \simplex$ and $r \in \R$ such that $p \in \gamma_r$.
%%	\begin{equation}
%%	\ccdim(\ell) \geq \|p\|_0 - \dim(\Sc_{\gamma_r}(p)) - 1~.~
%%	\end{equation}\jessiet{TODO: add minnability\bo{Tried!}}
\end{restatable}
\begin{proof}[Proof sketch]
	%\btw{Bo: rearranged the statements here a little, I felt the previous version required the reader to keep a bit more in their head.}
	\jessie{Redid this citing Lemma~\ref{lem:finite-relint-dim} instead}
	First, take $p \in \relint{\simplex}$ for intuition, so $\|p\|_0 = n$.
	Lemma~\ref{thm:convex-flats-inf-dim} guarantees the existence of a $d$-flat $F$ with $p \in F \subseteq \gamma_r$.
	Moreover, since $p \in \relint{\simplex}$, the flat $F$ satisfies the requirements of Lemma~\ref{lem:finite-relint-dim}, and the bound $\dim(\Sc_{\gamma_r}(p)) \geq \spn(F - \{p\}) \geq n - d- 1$ is given by chaining Lemma~\ref{lem:finite-relint-dim} (ii) and Lemma~\ref{lem:Fp-subset-feasible-subset}.
%	By Lemma~\ref{lem:Pcodim-codim-finite}, this implies the existence of a matrix $W$ such that $p \in \{q \in \simplex : Wq = \vec 0 \} = F \subseteq \gamma_r$ and $\codim(W) \leq d$.
%	%dimension at least $n-d-1$ with $p \in F$ and $F \cap \simplex \subseteq \gamma_r$. 
%	For $p \in \relint{\simplex}$, this implies that $\Sc_{\gamma_r}(p) \supseteq F - p$.
%	Moreover, this implies $\dim(\Sc_{\gamma_r}(p)) \geq \codim(W) = n - d - 1$, completing the proof for $p \in \relint{\simplex}$.

@@

\begin{lemma}\label{lem:finite-relint-dim}
  Let the $d$-flat $F\subseteq \P$ (defined over finite $\Y$) contain some $p\in\relint{\P}$.
  Then 
  \begin{enumerate}
  	\item[(i)] $p \in \relint{F}$; 
  	\item[(ii)] $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  %\raf{Moved; see margin comment:  for the function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.  (Such a function must exist by $F$ being a $d$-flat.)}

  As $F$ is a $d$-flat, we have some $W:\Y \to \reals^d$ such that $F = \zeros{W}$.
  Define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W:\spn(\P_p)\to\reals^d, v\mapsto \E_v W$.

  (i)
  Since $p \in \relint{\P}$, for all $q \in \P$, there is some small enough $\epsilon > 0 $ so that for all $\alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
  \jessiet{Probably a dumb question, but does this require $\P$ convex?}
  In particular, for $q \in F$, we claim $q_\alpha \in F$.
  %\raft{$V$ comes out of nowhere here, and then in the next bullet you introduce $W$ for the same thing. Better to do all that before both bullets. ``As $F$ is a $d$-flat, we have some $W$... $F=\zeros{W}$''.  Also, okay to just write $\E_p W$ not $\E_p W(Y)$, since technically $W$ is a random variable.}
  As $p,q \in F$, we have $\E_pW = \E_qW = \vec 0$.
  By linearity of expectation, we then have $\E_{q_\alpha} W = \vec 0$.
  % (Y) = \E_p V(Y) - \alpha(\E_q V(Y) - \E_p V(Y)) = \vec 0 - \alpha(\vec 0 - \vec 0) = \vec 0$.
  This implies $q_\alpha \in F$, and therefore $p \in \relint{F}$.

  (ii)
  We first show $\spn(F_p) = \ker(T_W)$.
%  Let $v \in \ker(T_W)$. % = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
%  From (i), as $p \in \relint{\P}$, we have $\vec 0 \in \relint{F_p}$.
%  Thus there is some $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$.
%  As $\epsilon v \in F_p$, and $v$ is a scalar multiple of it, we additionally conclude $v \in \spn(F_p)$.
%  Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
%  Hence, $\spn(F_p) = \ker(T_W)$.\jessie{Right?}\raf{Why? Hint: you want to show $v$ is in the span of $F_p$; in fact, it's a scalar multiple of something in $F_p$.}
%  
%  
  Let $v \in \spn(F_p)$.
  Then there is some $\alpha$ so that $\alpha v \in F_p$.
  This means $\E_{\alpha v} W = \vec 0$, which in turn implies $\alpha v \in \ker(T_W)$.
  By linearity of expectation, we additionally have $v \in \ker(T_W)$.
  Thus, $\spn(F_p) \subseteq \ker(T_W)$.

  Now let $v \in \ker(T_W)$, and $v' \in F_p$.
  This means $\E_v W = \vec 0$, so it suffices to show $v = c v' \in F_p$, thus showing $v \in \spn(F_p)$.
  Since $p \in \relint{\P}$, we must have $\vec 0 \in \relint{F_p}$, so we know there is some small enough $\epsilon > 0$ so that $-\alpha v' \in F_p$ for $\alpha \in (-\epsilon, \epsilon)$.
  Take $c = -\alpha$, and we conclude $v \in \spn(F_p)$.
  Therefore, $\ker(T_W) = \spn(F_p)$.

  As $\Y$ is a finite set, $\spn(\P_p)$ is a finite-dimensional vector space.
  The rank-nullity theorem states $\dim(\im(T_W)) + \dim(\ker(T_W)) = \dim(\spn(\P_p))$.
  As $\dim(\im(T_W)) \leq d$, and we have shown above that $\spn(F_p) = \ker(T_W)$, the conclusion follows.\raft{Worth checking the diff for what I changed. Inequality was backwards :-)} \jessiet{Lol saw this comment in the diff before I pulled...}
  % 
  %	Now let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
  %	There must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$ $p \in \relint{\P}$ implies $\vec 0 \in \relint{F_p}$ by (1.).
  %	Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
  %	This allows us to conclude $\spn(F_p) = \ker(T_W)$.\jessie{Right?}
  %	
  %	We want to show $F_p = \P_p \cap \ker(T_W)$, then derive the result from there. \jessie{I don't see why this is necessary.}
  %	
  %	In order to see this, consider $v \in F_p \iff v + p \in F$, and similarly for $\P_p$.
  %	Now, as $F \subseteq \P$ by construction, we have $F_p \subseteq \P_p$, and since $\spn(F_p) = \ker(T_W)$, we additionally have $F_p \subseteq \ker(T_W)$, yielding $F_p \subseteq \P_p \cap \ker(T_W)$.
  %	Now consider $v \in \P_p \cap \ker(T_W)$; we know that $\E_v W = \vec 0$, and therefore, $\E_{q} W = \vec 0$, so $v \in F_p$, thus $F_p = \P_p \cap \ker(T_W)$.
  %	
  %	Since $\spn(F_p) = \ker(T_W)$, we have $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(\P_p)) - d$ by \jessie{isomorphism theorem} since $F_p = \ker(T_W) \cap \P_p$. \jessie{??}
\end{proof}

\begin{lemma}\label{lem:Fp-subset-feasible-subset}
Suppose we are given $p \in \relint{\P}$, property $\gamma: \P \toto \R$, and report $r \in \gamma(p)$.
If $\gamma$ is indirectly elicited by a convex $L \in \L_d$, then there is a $d$-flat $F$ such that $p \in F$ and $F_p := F - \{p\} \subseteq \Sc_{\gamma_r}(p)$.	
\end{lemma}
\begin{proof}
	Construct $F$ as in Lemma~\ref{thm:convex-flats-inf-dim}; $F$ is a $d$-flat, contains $p$, and we have $F \subseteq \gamma_r$.
	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
	By Lemma~\ref{lem:finite-relint-dim}(i), we know $p \in \relint{F}$, and therefore, $\vec 0 \in \relint{F_p}$.
	Consider $v \in F_p$.
	By $F_p$ being convex and $\vec 0 \in \relint{F_p}$, we know there exists an $\alpha > 0$ so that $-\alpha v \in F_p$.
	This implies $p - \alpha v \in F \implies p - \alpha v \in \gamma_r \implies v \in \Sc_{\gamma_r}(p)$ since $F$ and $\Sc_{\gamma_r}(p)$ are convex and $F \subseteq \gamma_r$.
	This yields the desired result, $F_p \subseteq \Sc_{\gamma_r}(p)$.\raft{It feels weird how redundant this is from the argument in the 1st paragraph of (ii) above, but okay for now.}
\end{proof}

@@

Now, suppose for contradiction that $q \not\in \gamma_{r'}$.\jessiet{I think this can be made more concise, but is clearest this way; it's a bit tricky with the movement between discussing flats and hyperplanes and being subsets of level sets, etc.}
Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
This contradicts the assumption $F \subseteq \gamma_r$.
Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
Because $r$ and $r'$ were completely symmetric, this completes the proof.
%
% %commented out 01.22.2021 - Jessie; incorporating Lemma that says p in relint(F)	
%	Suppose $F \subseteq \gamma_r$.
%	We show $F \subseteq \gamma_{r'}$.
%	Let $q \in F$.
%	We claim that for small enough $\epsilon$, the point $q' = p - \epsilon (q-p)$ is in $F$ as well.
%	Containment in $F$ follows because both $p$ and $q$ are in $F$ and it is a flat, while containment in $\P$ follows because $p \in \relint\P$. \jessie{Does $\relint{F}$ actually come in here?}
%	
%	Now, suppose for contradiction that $q \not\in \gamma_{r'}$.
%	Then $v \cdot q < 0$: containment in $\gamma_r$ gives $v \cdot q \leq 0$, and if $v \cdot q = 0$ then $q \in \gamma_r \cap H \implies q \in \gamma_{r'}$, a contradiction.
%	But, noting that $p \in H$, we have $v \cdot q' = -\epsilon (v \cdot q) > 0$, so $q'$ is not in $\gamma_{r}$.
%	This contradicts the assumption $F \subseteq \gamma_r$.
%	Therefore, we must have $q \in \gamma_{r'}$, so we have shown $F \subseteq \gamma_{r'}$.
%	Because $r$ and $r'$ were completely symmetric, this completes the proof.
\end{proof}

@@

\hariresult*
\begin{proof}
	Let $L : \reals^d \times \Y \to \reals$ elicit $\Gamma$ be a calibrated surrogate for $\ell$, and consider $\Y^{\proj(q)} := \supp(q)$ for any $q \in \simplex$ and what happens when we restrict $L$ and $\ell$ to only the outcomes in $\Y^{\proj(q)}$.
	Take $L^{\proj(q)} := L|_{\Y^{\proj(q)}}$ and $\ell^{\proj(q)} := \ell|_{\Y^{\proj(q)}}$.
	In particular, take $\Y' = \Y^{\proj(p)}, L' = L^{\proj(p)}$, and $\ell' = \ell^{\proj(p)}$. 
	By calibration, we have $L$ indirectly eliciting $\gamma$.

	Now, observe $L'$ (eliciting $\Gamma'$) indirectly elicits $\gamma' := \prop[\simplexp]{\ell'}$ since, for all $q \in \simplex$, taking $P(q) \in \simplexp$ to be $q$ projected onto $\simplexp$ by removing $0$ entries of $q$, and letting $p' = P(p)$, we have $p' \in \Gamma'_u \implies p' \in \gamma'_{\psi(u)}$.
	Moreover, $\Gamma(p) = \Gamma'(p')$ and $\gamma(p) = \gamma'(p')$.
	This same observation can be used to observe that $L'$ is also calibrated with respect to $\ell'$ as the calibration bound holds for all $q \in \simplex$, and therefore for all $P(q)$ by equality of $\gamma(q) = \gamma^{\proj(q)}(P(q))$.

	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a $d$-flat $F$ with $p' \in F \subseteq \gamma'_r$.
	Taking $\P = \simplexp$, we know $p' \in \relint{\simplexp}$ by construction, so we can apply Lemma~\ref{lem:finite-relint-dim}(ii), which gives $\dim(\spn(F_{p'})) \geq \dim(\spn(\P_{p'})) - d$.
	Since $\P = \simplexp$ and $p' \in \relint{\simplexp}$, we have $\dim(\spn(\P_{p'})) = \dim(\affhull(\simplexp)) = \|p\|_0 - 1$.
	Therefore, $\dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$\raft{Might be nicer on the reader to add one more step for $\|p\|_0$. Also, I just realized we are using $p\in\simplex$ here, but then $p$ can't be in $F\subseteq\Delta_{\Y'}$ ($p$ is an $n$-vector). So maybe we need a $p'$ too.}.
	Moreover, $F_{p'} \subseteq \Sc_{\gamma'_r}(p')$ since $p' \in \relint{F}$ by Lemma~\ref{lem:Fp-subset-feasible-subset}.
	By Lemma~\ref{lem:p-boundary-fsd}, we additionally have $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p')$.
	Chaining these results, we obtain 
	\begin{align*}
	\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p'))  &\geq \dim(F_{p'}) = \dim(\spn(F_{p'})) \geq \|p\|_0 - 1 - d~.~
	\end{align*}
%
%	this yields the bound $\dim(\spn(F-\{p\})) \geq \|p\|_0 - 1 - d$.
%	Chaining inequalities, we then have $\dim(\Sc_{\gamma'_r}(p)) \geq \dim(\spn(F - \{p\})) \geq \|p\|_0 - d- 1$ as Lemma~\ref{lem:feas-sub-is-a-flat} states $F - \{p\}$ is a subspace of $\Sc_{\gamma'_r}(p)$.
%	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
	%
	%
	%\old version of the proof from NeurIPS or before - 01.21.2021
	%	First, for intuition, consider $p \in \relint{\simplex}$. 
	%	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
	%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\Sc_{\gamma_r}(p)) - 1$.
	%
	%	
	%	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
	%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and thus the result holds.
	%	
	%	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
	%	\begin{align*}
	%		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
	%	\end{align*}
	%	Therefore, we have $L'$ calibrated with respect to $\ell'$.
	%
	%	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
	%	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
	%	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
	%	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
	%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
\end{proof}
